STA610 Case Study 1 Team 4 Report

### 2021-03-22 STA_610_Case_Study_1_Report_Team_4.Rmd
formatted the EDA sections.

We renamed this variable `dose_per_mg` to make its meaning clearer to the reader. This is a continuous variable that nevertheless tends to take on only a few values, as depicted in the histogram. We considered a recoding of this variable into levels, but decided against it as the dose per milligram technically may take on any value and the generalizability of our model may be improved if we are able to consider dose levels that are in a realistic range yet not present in our current data.

```{r, fig.align='center', fig.height=2.5}
ggplot(df, aes(x=mgstr)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white", bins = 50)+
 geom_density(alpha=.2, fill="red") +
labs(x="does per mg",y="density")
# rename variable for ease of interpretability
df <- df %>% rename(dose_per_mg = mgstr)
```

@@

### dose_per_mg
```{r, fig.align='center', fig.height = 2.5}
ggplot(data = df[df$state=="Florida" | df$state=="Texas" | df$state=="North Carolina",], aes(x = dose_per_mg, y = log_ppm)) + 
  geom_point() +
  facet_grid(~ state)
```

### date_num
```{r, fig.align='center', fig.height = 2.5}
ggplot(data = df[df$state=="Florida" | df$state=="Texas" | df$state=="North Carolina",], aes(x = date_num, y = log_ppm)) + 
  geom_point() +
  facet_grid(~ state)
```

@@

### bulk_purchase
```{r, fig.align='center', fig.height = 2.5}
# categorical variables -- looking at South only
set.seed(42)
states <- sample(df$state, 5)
ggplot(data = df %>% filter(state %in% states), aes(x = bulk_purchase, y = log_ppm)) + 
  geom_boxplot() +
  facet_grid(~ state) +
  theme(axis.text.x = element_text(angle = 90))
```

### date_quarter
```{r, fig.height = 2.5, fig.align='center'}
ggplot(data = df[df$state=="Florida" | df$state=="Texas" | df$state=="North Carolina",], aes(x = date_quarter, y = log_ppm, group = date_quarter)) + 
  geom_boxplot() +
  facet_grid(~ state)
```

### Primary_Reason
```{r, fig.height = 2.5, fig.align='center'}
ggplot(data = df[df$state=="Florida" | df$state=="Texas" | df$state=="North Carolina",], aes(x = Primary_Reason, y = log_ppm, group = Primary_Reason)) + 
  geom_boxplot() +
  facet_grid(~ state) +
  theme(axis.text.x = element_text(angle = 90))
```

### source
```{r, fig.height = 2.5, fig.align='center'}
ggplot(data = df[df$state=="Florida" | df$state=="Texas" | df$state=="North Carolina",], aes(x = source, y = log_ppm, group = source)) + 
  geom_boxplot() +
  facet_grid(~ state) + 
  theme(axis.text.x = element_text(angle = 90))
```

>>>>

We renamed this variable `dose_per_mg` to make its meaning clearer to the reader. This is a continuous variable that nevertheless tends to take on only a few values. We considered a recoding of this variable into levels, but decided against it as the dose per milligram technically may take on any value and the generalizability of our model may be improved if we are able to consider dose levels that are in a realistic range yet not present in our current data.

```{r, fig.align='center', fig.height=2, include = FALSE}
ggplot(df, aes(x=mgstr)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white", bins = 50)+
 geom_density(alpha=.2, fill="red") +
labs(x="does per mg",y="density")
# rename variable for ease of interpretability
df <- df %>% rename(dose_per_mg = mgstr)
```

@@

### dose_per_mg & date_num
```{r, fig.align='center', fig.height = 2.5}
plot_dose_per_mg <- ggplot(data = df[df$state=="Florida" | df$state=="Texas" | df$state=="North Carolina",], aes(x = dose_per_mg, y = log_ppm)) + 
  geom_point() +
  facet_grid(~ state)
```

```{r, fig.align='center', fig.height = 2.5}
plot_date_num <- ggplot(data = df[df$state=="Florida" | df$state=="Texas" | df$state=="North Carolina",], aes(x = date_num, y = log_ppm)) + 
  geom_point() +
  facet_grid(~ state)

grid.arrange(plot_dose_per_mg, plot_date_num, ncol = 2)
```

@@

### bulk_purchase & date_quarter
```{r, fig.align='center', fig.height = 2.5}
# categorical variables -- looking at South only
set.seed(42)
states <- sample(df$state, 5)
box_bulk_purchase <- ggplot(data = df[df$state=="Florida" | df$state=="Texas" | df$state=="North Carolina",], aes(x = bulk_purchase, y = log_ppm, group = bulk_purchase)) + 
  geom_boxplot() +
  facet_grid(~ state) +
  theme(axis.text.x = element_text(angle = 90))
```

```{r, fig.height = 2.5, fig.align='center'}
box_date_quarter <- ggplot(data = df[df$state=="Florida" | df$state=="Texas" | df$state=="North Carolina",], aes(x = date_quarter, y = log_ppm, group = date_quarter)) + 
  geom_boxplot() +
  facet_grid(~ state)

grid.arrange(box_bulk_purchase, box_date_quarter, ncol=2)
```

### Primary_Reason & source
```{r, fig.height = 2.5, fig.align='center'}
box_Primary_Reason <- ggplot(data = df[df$state=="Florida" | df$state=="North Carolina",], aes(x = Primary_Reason, y = log_ppm, group = Primary_Reason)) + 
  geom_boxplot() +
  facet_grid(~ state) +
  theme(axis.text.x = element_text(angle = 90))
```

```{r, fig.height = 2.5, fig.align='center'}
box_source <- ggplot(data = df[df$state=="Florida" | df$state=="North Carolina",], aes(x = source, y = log_ppm, group = source)) + 
  geom_boxplot() +
  facet_grid(~ state) + 
  theme(axis.text.x = element_text(angle = 90))

grid.arrange(box_Primary_Reason, box_source, ncol = 2)
```
